Objective-first optimization for nanophotonics

### 2012-07-10 presentations/meta_book/extensions.tex
Sent draft to Ken.

\section{Extending the method}
The objective-first method, as applied in the examples in this chapter,
    really only represent a small foray into the area of nanophotonic design.
Several key extensions to what is presented here are needed to
    fully address real-world nanophotonic design challenges.

@@

Tractable approaches include penalizing intermediate values of $p$\cite{simp}
    or even transferring to a level-set method\cite{miller}
    where the distinction between materials is explicit.

>>>>

\section{Extending the method}
The objective-first method, as applied in the examples in this chapter,
    represents only a small foray into the area of nanophotonic design.
Several key extensions to what is presented here are needed to
    fully address real-world nanophotonic design challenges.

@@

Tractable approaches include penalizing intermediate values of $p$ \cite{simp}
    or even transferring to a level-set method \cite{miller}
    where the distinction between materials is explicit.
